Hidden Talents Multiverse Analysis

### 2021-06-28 README.Rmd
makeing sure markdown tables are displayed in OSF

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "data-prep") %>% 
  select(-dir) %>% 
  knitr::kable(format = "pipe")
```

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "primary-analyses") %>% 
  select(-dir) %>% 
  knitr::kable(format = "pipe")
```

@@

```{r}
file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "secondary-analyses") %>% 
  select(-dir) %>% 
  knitr::kable(format = "pipe")
```

>>>>

```{r, results='asis'}
data_prep <- 
  file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "data-prep") %>% 
  select(-dir)

cat(
  "|script|input|output|",
  "|------|-----|------|",
  glue::glue_data(
    data_prep,
    "|{script}|{input}|{output}|"
  ),
  sep = "\n"
)
```

@@

```{r, results='asis'}
primary_analyses <- 
  file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "primary-analyses") %>% 
  select(-dir)

cat(
  "|script|input|output|",
  "|------|-----|------|",
  glue::glue_data(
    primary_analyses,
    "|{script}|{input}|{output}|"
  ),
  sep = "\n"
)
```

@@

```{r, results='asis'}
secondary_analyses <- 
  file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "secondary-analyses") %>% 
  select(-dir)

cat(
  "|script|input|output|",
  "|------|-----|------|",
  glue::glue_data(
    secondary_analyses,
    "|{script}|{input}|{output}|"
  ),
  sep = "\n"
)
```
